### 2014-09-29 Conclusions.tex
minor rephrase of conclusions

We show that magnetic reconstruction EFIT++ with linear $p'$ and $FF'$ features a relatively good accuracy of 1 -- 2 cm in the plasma shape reconstruction but introduces a systematic error in internal plasma parameters, such as $W$, $l_{\mathrm i}$, $\beta_{\mathrm p}$ or $q_0$. The reconstruction properties can be significantly improved by using quadratic $p'$ for diverted plasmas, which removes the systematic error and also improves the LCFS reconstruction. EFIT++ converges in 100~\% cases in this regime.

>>>>

We show that magnetic reconstruction EFIT++ with linear $p'$ and $FF'$ features a relatively good accuracy of 1 -- 2 cm in the plasma shape reconstruction but introduces systematic errors both in the shape and in internal plasma parameters, such as $W$, $l_{\mathrm i}$, $\beta_{\mathrm p}$ or $q_0$. The reconstruction properties can be significantly improved by using quadratic $p'$ for divertor plasmas, which removes the systematic error and also improves the LCFS reconstruction. EFIT++ converges in 100~\% cases in this regime.
